Bound within Boundaries: How Well Do Protected Areas Match Movement Corridors of Their Most Mobile Protected Species?

### 2020-09-02 Chapter_0/04_Manuscript/99_PermeabilityModelAICs.tex
Worked on the revision for BES paper

% latex table generated in R 3.6.3 by xtable 1.8-4 package
% Thu Jun  4 15:54:16 2020
\begin{tabular}{lrrrr}
  \toprule
Covariates & AIC & DeltaAIC & Weight & LogLik \\ 
  \midrule
cos(ta) + log(sl) + W + T + DTW + HB5 + S & 90091.40 & 0.00 & 1.00 & -45030.70 \\ 
  cos(ta) + log(sl) + W + T + DTW + HB5 + S + DTR & 90093.51 & 2.11 & 0.00 & -45029.75 \\ 
  cos(ta) + log(sl) + W + T + DTW + HB5 & 90094.79 & 3.38 & 0.00 & -45034.39 \\ 
  cos(ta) + log(sl) + W + T + DTW + HB5 + S + P & 90095.05 & 3.65 & 0.00 & -45030.52 \\ 
  cos(ta) + log(sl) + W + T + DTW + S & 90096.95 & 5.55 & 0.00 & -45035.47 \\ 
  cos(ta) + log(sl) + W + T + DTW + HB5 + DTR & 90097.02 & 5.62 & 0.00 & -45033.51 \\ 
  cos(ta) + log(sl) + W + T + DTW + HB5 + S + DTR + P & 90097.38 & 5.98 & 0.00 & -45029.69 \\ 
  cos(ta) + log(sl) + W + T + DTW + HB5 + S + RC & 90097.53 & 6.13 & 0.00 & -45029.76 \\ 
  cos(ta) + log(sl) + W + T + DTW + HB5 + P & 90098.46 & 7.06 & 0.00 & -45034.23 \\ 
  cos(ta) + log(sl) + W + T + DTW + HB5 + S + DTR + RC & 90099.62 & 8.22 & 0.00 & -45028.81 \\ 
  cos(ta) + log(sl) + W + T + DTW & 90099.97 & 8.57 & 0.00 & -45038.99 \\ 
  cos(ta) + log(sl) + W + T + DTW + HB5 + RC & 90100.68 & 9.28 & 0.00 & -45033.34 \\ 
  cos(ta) + log(sl) + W + T + DTW + DTR & 90101.68 & 10.28 & 0.00 & -45037.84 \\ 
  cos(ta) + log(sl) + W + T + DTW + P & 90103.07 & 11.67 & 0.00 & -45038.54 \\ 
  cos(ta) + log(sl) + W + T + DTW + HB5 + S + DTR + P + RC & 90103.48 & 12.08 & 0.00 & -45028.74 \\ 
  cos(ta) + log(sl) + W + T + DTW + RC & 90104.72 & 13.32 & 0.00 & -45037.36 \\ 
  cos(ta) + log(sl) + W + T + HB5 & 90123.71 & 32.31 & 0.00 & -45050.85 \\ 
  cos(ta) + log(sl) + W + T & 90128.17 & 36.77 & 0.00 & -45055.09 \\ 
  cos(ta) + log(sl) + W + T + S & 90129.36 & 37.96 & 0.00 & -45053.68 \\ 
  cos(ta) + log(sl) + W + T + DTR & 90130.11 & 38.71 & 0.00 & -45054.05 \\ 
  cos(ta) + log(sl) + W + T + P & 90131.75 & 40.35 & 0.00 & -45054.88 \\ 
  cos(ta) + log(sl) + W + T + RC & 90133.53 & 42.13 & 0.00 & -45053.77 \\ 
  cos(ta) + log(sl) + W + DTW & 90138.92 & 47.52 & 0.00 & -45060.46 \\ 
  cos(ta) + log(sl) + W + HB5 & 90149.30 & 57.90 & 0.00 & -45065.65 \\ 
  cos(ta) + log(sl) + W + S & 90151.14 & 59.74 & 0.00 & -45066.57 \\ 
  cos(ta) + log(sl) + W & 90153.70 & 62.30 & 0.00 & -45069.85 \\ 
  cos(ta) + log(sl) + W + DTR & 90156.32 & 64.92 & 0.00 & -45069.16 \\ 
  cos(ta) + log(sl) + W + P & 90157.23 & 65.83 & 0.00 & -45069.62 \\ 
  cos(ta) + log(sl) + W + RC & 90159.32 & 67.91 & 0.00 & -45068.66 \\ 
  cos(ta) + log(sl) + S & 90161.07 & 69.67 & 0.00 & -45073.54 \\ 
  cos(ta) + log(sl) + DTW & 90262.03 & 170.63 & 0.00 & -45124.01 \\ 
  cos(ta) + log(sl) + T & 90301.56 & 210.16 & 0.00 & -45143.78 \\ 
  cos(ta) + log(sl) + HB5 & 90307.55 & 216.15 & 0.00 & -45146.78 \\ 
  cos(ta) + log(sl) + DTR & 90316.37 & 224.97 & 0.00 & -45151.19 \\ 
  cos(ta) + log(sl) + P & 90316.62 & 225.22 & 0.00 & -45151.31 \\ 
  cos(ta) + log(sl) + RC & 90318.46 & 227.06 & 0.00 & -45150.23 \\ 
   \bottomrule
\end{tabular}

>>>>

% latex table generated in R 3.6.3 by xtable 1.8-4 package
% Wed Sep  2 09:04:38 2020
\begin{tabular}{lrrrr}
  \toprule
Covariates & AIC & DeltaAIC & Weight & LogLik \\ 
  \midrule
cos(ta) + sl + log(sl) + W + T + DTW + HI + S & 90068.15 & 0.00 & 1.00 & -45017.08 \\ 
  cos(ta) + sl + log(sl) + W + T + DTW + HI & 90071.84 & 3.69 & 0.00 & -45020.92 \\ 
  cos(ta) + sl + log(sl) + W + T + DTW + HI + S + DTR & 90071.94 & 3.79 & 0.00 & -45016.97 \\ 
  cos(ta) + sl + log(sl) + W + T + DTW + HI + S + P & 90071.94 & 3.79 & 0.00 & -45016.97 \\ 
  cos(ta) + sl + log(sl) + W + T + DTW + HI + S + RC & 90073.46 & 5.30 & 0.00 & -45015.73 \\ 
  cos(ta) + sl + log(sl) + W + T + DTW + HI + DTR & 90075.66 & 7.50 & 0.00 & -45020.83 \\ 
  cos(ta) + sl + log(sl) + W + T + DTW + HI + P & 90075.66 & 7.51 & 0.00 & -45020.83 \\ 
  cos(ta) + sl + log(sl) + W + T + DTW + HI + S + DTR + P & 90075.79 & 7.64 & 0.00 & -45016.89 \\ 
  cos(ta) + sl + log(sl) + W + T + DTW + S & 90076.71 & 8.56 & 0.00 & -45023.36 \\ 
  cos(ta) + sl + log(sl) + W + T + DTW + HI + RC & 90076.84 & 8.69 & 0.00 & -45019.42 \\ 
  cos(ta) + sl + log(sl) + W + T + DTW + HI + S + DTR + RC & 90077.20 & 9.05 & 0.00 & -45015.60 \\ 
  cos(ta) + sl + log(sl) + W + T + DTW & 90080.08 & 11.92 & 0.00 & -45027.04 \\ 
  cos(ta) + sl + log(sl) + W + T + DTW + HI + S + DTR + P + RC & 90080.96 & 12.81 & 0.00 & -45015.48 \\ 
  cos(ta) + sl + log(sl) + W + T + DTW + DTR & 90082.95 & 14.79 & 0.00 & -45026.47 \\ 
  cos(ta) + sl + log(sl) + W + T + DTW + P & 90083.31 & 15.16 & 0.00 & -45026.66 \\ 
  cos(ta) + sl + log(sl) + W + T + HI & 90103.28 & 35.13 & 0.00 & -45038.64 \\ 
  cos(ta) + sl + log(sl) + W + T & 90109.40 & 41.25 & 0.00 & -45043.70 \\ 
  cos(ta) + sl + log(sl) + W + T + S & 90110.35 & 42.20 & 0.00 & -45042.17 \\ 
  cos(ta) + sl + log(sl) + W + T + DTR & 90112.55 & 44.40 & 0.00 & -45043.27 \\ 
  cos(ta) + sl + log(sl) + W + T + P & 90113.11 & 44.96 & 0.00 & -45043.56 \\ 
  cos(ta) + sl + log(sl) + W + T + RC & 90113.60 & 45.45 & 0.00 & -45041.80 \\ 
  cos(ta) + sl + log(sl) + W + DTW & 90118.55 & 50.40 & 0.00 & -45048.28 \\ 
  cos(ta) + sl + log(sl) + W + HI & 90128.70 & 60.54 & 0.00 & -45053.35 \\ 
  cos(ta) + sl + log(sl) + W + S & 90132.22 & 64.06 & 0.00 & -45055.11 \\ 
  cos(ta) + sl + log(sl) + W & 90134.85 & 66.69 & 0.00 & -45058.42 \\ 
  cos(ta) + sl + log(sl) + W + DTR & 90138.31 & 70.16 & 0.00 & -45058.16 \\ 
  cos(ta) + sl + log(sl) + W + P & 90138.50 & 70.35 & 0.00 & -45058.25 \\ 
  cos(ta) + sl + log(sl) + W + RC & 90139.30 & 71.15 & 0.00 & -45056.65 \\ 
  cos(ta) + sl + log(sl) + S & 90141.98 & 73.83 & 0.00 & -45061.99 \\ 
  cos(ta) + sl + log(sl) + DTW & 90225.64 & 157.49 & 0.00 & -45103.82 \\ 
  cos(ta) + sl + log(sl) + T & 90271.73 & 203.58 & 0.00 & -45126.86 \\ 
  cos(ta) + sl + log(sl) + HI & 90273.18 & 205.02 & 0.00 & -45127.59 \\ 
  cos(ta) + sl + log(sl) + P & 90285.24 & 217.08 & 0.00 & -45133.62 \\ 
  cos(ta) + sl + log(sl) + DTR & 90285.33 & 217.18 & 0.00 & -45133.67 \\ 
  cos(ta) + sl + log(sl) + RC &  &  & 0.00 &  \\ 
  cos(ta) + sl + log(sl) + W + T + DTW + RC &  &  & 0.00 &  \\ 
   \bottomrule
\end{tabular}

### 2020-09-02 Chapter_0/04_Manuscript/Manuscript.tex
Worked on the revision for BES paper

\subsection{GPS Relocation Data}
We used a population of free-ranging African wild dogs inhabiting the Okavango
Delta in northern Botswana as a source population for dispersing individuals.
This population has been extensively studied since 1989 \citep{McNutt.1996,
Cozzi.2013, Cozzi.2020, Behr.2020}. Between 2011 and 2019, we systematically
collected GPS relocation data on 16 coalitions of dispersing African wild dogs
(7 female and 9 male coalitions). Candidate dispersing individuals were
identified based on age, number of same‐sex siblings, pack size, and presence of
unrelated individuals of the opposite sex in ther pack citep \citep{McNutt.1996,
Behr.2020}\todo{We originally only pointed to Behr and did not include the
criteria. The editor desired to include those}. Individuals were immobilized
according to protocols described in \cite{Osofsky.1996}, and fitted with
GPS/Satellite radio collars (\textit{Vertex Lite; Vectronic Aerospace GmbH,
Berlin, Germany}) while still with their natal pack. All procedures were
undertaken and supervised by a Botswana-registered wildlife veterinarian. Fully
assembled collars produced a tag weight of approximately xx kg, which conforms
to the proposed threshold of 3\% of an animal's body weight
\citep{Kenward.2000}. Collars were mounted using leather belts and included a
drop off mechanism triggered by a slowly decomposing piece of cloth.\todo{Editor
desired more information on GPS collar} During dispersal, GPS collars were
programmed to record GPS relocation data every 4 hours and to regularly transmit
them via Iridium satellite system to a base station.

@@

\subsection{Spatial Covariates}
To investigate habitat relative selection strength\todo{As per reviewer 1} of
dispersing wild dogs, we used a set of geo-referenced covariates
(\Cref{Covariates}) that we aggregated in the categories \textit{land cover}
(which included water cover, distance to water, shrubs/grassland cover, and tree
cover), \textit{protection status} (protected vs. unprotected), and
\textit{human pressure} (which included human density, presence of roads, and
distance to roads). For each of these covariates we prepared spatial raster
layers from freely available online services or from remotely sensed satellite
imagery. To ensure a consistent resolution (i.e. cell-size or grain) across
covariates, we coarsened or interpolated all layers to match a resolution of
250m x 250m. For further details on the preparation of each covariate, see
Appendix A.3. We performed processing and manipulation of data as well as all
spatial and statistical analyses using R, version 3.6.1 \citep{R.2019}.

@@

\noindent The selection score \(w(x)\) of a step depended on its associated
covariates (\(x_1, x_2, ..., x_n\)), as well as on the animal's relative
selection strength \todo{As per reviewer 1} for these covariates (\(\beta_1,
\beta_2, ..., \beta_n\)). To estimate relative selection strengths \todo{As per
reviewer 1} (i.e. the \(\beta\)'s), we used mixed effects conditional logistic
regression analysis as suggested by \cite{Muff.2020}. We implemented their
method using the R-package \textit{glmmTMB} \citep{Mollie.2017} and used
dispersing coalition ID to model random slopes. We also modeled random
intercepts with an arbitrary high variance of 1e6 to make use of the
\textit{poisson trick} (see \cite{Muff.2020}). We defined three movement
metrics, namely the cosine of the turning angle (\(cos(ta)\)), the step length
\(sl_\) and the natural logarithm of the step length (\(log(sl)\)), as core
covariates and ran stepwise forward model selection based on Akaike's
Information Criterion (AIC; \citealp{Burnham.2002}) for all other
covariates.\todo{Reviewer 1 asked for more details in the random effects. I
therefore decided to update this section too} The inclusion of movement metrics
served to reduce biases in estimated habitat selection coefficients \todo{as per
revierwer 1} that may have arisen due to movement behavior \citep{Avgar.2016}.
To validate the predictive power of the most parsimonious habitat selection
model, we ran k-fold cross-validation for case-control studies as described in
\cite{Fortin.2009} (details in Appendix A.5).

@@

\subsection{Least-Cost Paths and Corridors}
To identify movement corridors of dispersing wild dogs, we specified source
points and calculated factorial least-cost paths (LCPs) as well as factorial
least-cost corridors (LCCs) among them \citep{Elliot.2014}. We generated source
points by overlaying the study area with a regular grid of points spaced at 100
km. We only considered those points that fell within protected areas \(>\) 700
km\textsuperscript{2}, which conforms with home-range requirements of African
wild dogs reported in \cite{Pomilia.2015}. Finally, we defined centroids as
source points for those protected areas \(>\) 700 km\textsuperscript{2} that
were not assigned any source points from the regular grid. In total, we
generated 68 source points, which resulted in 2'278 unique pairwise combinations
and therefore 2'278 unique LCPs and LCCs. We computed factorial LCPs and LCCs
between source points using the R-package \textit{gdistance} (for further
details see Appendix A.6). After computation, we tallied overlapping LCPs and
LCCs, respectively, into single connectivity maps.

\section{Results}
\subsection{Dispersal Events}
In total, we collected 4'169 GPS relocations during dispersal (Figure S2 \&
Table S1), resulting in an average of 261 (\(SD\) = 207) locations per
dispersing coalition. Dispersers on dispersed on average for 48 days (\(SD\) =
44), covered a mean euclidean distance of 54 km (\(SD\) = 71) and a cumulative
distance of 597 km (\(SD\) = 508). One female coalition dispersed far east into
the Hwange Hwange National Park and covered a cumulative distance of over 360 km
in under 9 days.\todo{Editor desired a quick summary of the dispersal data.}

\subsection{Habitat Selection Model}
Our most parsimonious habitat selection model (\(\Delta AIC > 2\) than any
alternative model; Table S4) retained the covariates \textit{water},
\textit{distance to water}, \textit{trees}, \textit{shrubs/grassland}, and
\textit{human influence}, beside the fixed covariates \textit{cos(ta)} and
\textit{log(sl)} (\Cref{PermeabilityResults}a). The positive coefficient for
\(log(sl)\) (\(\beta\) = 0.06, 95\% CI = 0.02 to 0.09) showed that our fitted
(yet selection-biased) gamma distribution produced step-lengths slightly shorter
than under a selection-free gamma distribution. Similarly, the positive
coefficient for \(cos(ta)\) (\(\beta\) = 0.14; 95\% CI = 0.07 to 0.21) indicates
that the uniform distribution for turning angles produced turning angles with
too little directionality.\todo{Reviewer 1 nicely explained that the
coefficients for log(sl) and cos(ta) imply that the initial distributions were
selection-biased} With respect to environmental covariates, dispersers avoided
moving through water (\(\beta\) = -0.52, 95\% CI -0.77 to -0.26) but selected
for locations in its vicinity, although the latter effect was not significant
(\(\beta\) = -0.32, 95\% CI = -0.72 to 0.08). Dispersers avoided areas that were
densely covered by trees (\(\beta\) = -0.31, CI = -0.46 to -0.15) and preferred
areas covered by shrubs/grassland (\(\beta\) = 0.25, 95\% CI = 0.07 to 0.42).
Finally, dispersers avoided areas that were influenced by humans (\(\beta\) =
-0.41, 95\% CI = -0.78 to -0.05).

@@

\begin{table}[h]
  \begin{center}
  \caption{Comparison of median permeability (interquantile range in brackets)
  across countries, separated into areas within and outside the KAZA-TFCA, as
  well as within and outside formally protected areas. High values indicate high
  permeability, whereas low values correspond to low permeability.}
  \label{PermeabilityComp}
  \begin{tabular}{llllll}
    \toprule
    \multicolumn{1}{c}{} & \multicolumn{2}{c}{KAZA-TFCA} &
    \multicolumn{2}{c}{Protection Status} & \multicolumn{1}{c}{} \\
    \cmidrule(l{3pt}r{3pt}){2-3} \cmidrule(l{3pt}r{3pt}){4-5}
    Country & Inside & Outside & Protected & Pastoral & Overall\\
    \midrule
    Angola & 0.36 (0.41) & 0.12 (0.32) & 0.36 (0.41) & 0.12 (0.33) & 0.20 (0.39)\\
    Botswana & 0.25 (0.30) & 0.15 (0.16) & 0.28 (0.35) & 0.15 (0.18) & 0.19 (0.25)\\
    Namibia & 0.22 (0.30) & 0.13 (0.18) & 0.24 (0.30) & 0.11 (0.15) & 0.16 (0.24)\\
    Zambia & 0.05 (0.09) & 0.03 (0.06) & 0.04 (0.10) & 0.03 (0.05) & 0.03 (0.07)\\
    Zimbabwe & 0.07 (0.16) & 0.06 (0.05) & 0.08 (0.17) & 0.05 (0.05) & 0.06 (0.07)\\
    \hline
    Overall & 0.16 (0.30) & 0.07 (0.15) & 0.15 (0.30) & 0.07 (0.15) & 0.10 (0.22)\\
    \bottomrule
  \end{tabular}
  \end{center}
\end{table}

>>>>

\subsection{GPS Relocation Data}
We used a population of free-ranging African wild dogs inhabiting the Okavango
Delta in northern Botswana as a source population for dispersing individuals.
This population has been extensively studied since 1989 \citep{McNutt.1996,
Cozzi.2013, Cozzi.2020, Behr.2020}. Between 2011 and 2019, we systematically
collected GPS relocation data on 16 coalitions of dispersing African wild dogs
(7 female and 9 male coalitions). Candidate dispersing individuals were
identified based on age, number of same‐sex siblings, pack size, and presence of
unrelated individuals of the opposite sex in ther pack citep \citep{McNutt.1996,
Behr.2020}\todo{We originally only pointed to Behr and did not include the
criteria. The editor desired to include those}. Individuals were immobilized
according to protocols described in \cite{Osofsky.1996}, and fitted with
GPS/Satellite radio collars (\textit{Vertex Lite; Vectronic Aerospace GmbH,
Berlin, Germany}) while still with their natal pack. All procedures were
undertaken and supervised by a Botswana-registered wildlife veterinarian. Fully
assembled collars produced a tag weight of approximately 330 g, accounting for
approximately 1.2\% of a wild dog's average body weight. Collars were mounted
using leather belts and included a drop off mechanism, triggered by a slowly
decomposing piece of cloth.\todo{Editor desired more information on GPS collar}
During dispersal, GPS collars were programmed to record GPS relocation data
every 4 hours and to regularly transmit them via Iridium satellite system to a
base station.

@@

\subsection{Spatial Covariates}
To investigate relative selection strengths \todo{As per reviewer 1} of
dispersing wild dogs, we used a set of geo-referenced covariates
(\Cref{Covariates}) that we aggregated in the categories \textit{land cover},
\textit{protection status}, and \textit{human influence}. Land cover comprised
of the covariates water cover, distance to water, percentage cover by
shrubs/grassland, and percentage cover by trees. To capture the pulsing behavior
of the Okavango Delta we frequently updated water cover layers and corresponding
distance to water layers. Protection status contained a binary indicator of
whether an area was protected or not. Human influence included covariates
rendering human density, the presence of roads, and the distance to
roads.\todo{Reviewer 2 found the description of the covariates unclear} For each
of these covariates we prepared spatial raster layers from freely available
online services or from remotely sensed satellite imagery. To ensure a
consistent resolution (i.e. cell-size or grain) across covariates, we coarsened
or interpolated all layers to match a resolution of 250m x 250m. For further
details on the preparation of each covariate, see Appendix A.3. We performed
processing and manipulation of data as well as all spatial and statistical
analyses using R, version 3.6.1 \citep{R.2019}.

@@

\noindent The selection score \(w(x)\) of a step depended on its associated
covariates (\(x_1, x_2, ..., x_n\)), as well as on the animal's relative
selection strength \todo{As per reviewer 1} for these covariates (\(\beta_1,
\beta_2, ..., \beta_n\)). To estimate relative selection strengths \todo{As per
reviewer 1} (i.e. the \(\beta\)'s), we used mixed effects conditional logistic
regression analysis as suggested by \cite{Muff.2020}. We implemented their
method using the R-package \textit{glmmTMB} \citep{Mollie.2017} and used
dispersing coalition ID to model random slopes. We also modelled random
intercepts with an arbitrary high variance of 10\textsuperscript{6} to make use
of the poisson trick (see \citealp{Muff.2020}). We defined three movement
metrics, namely the cosine of the turning angle (\(cos(ta)\)), the step length
(\(sl\)) and the natural logarithm of the step length (\(log(sl)\)), as core
covariates and ran stepwise forward model selection based on Akaike's
Information Criterion (AIC; \citealp{Burnham.2002}) for all other
covariates.\todo{Reviewer 1 asked for more details in the random effects. I
therefore decided to update this section too} The inclusion of movement metrics
served to reduce biases in estimated habitat selection coefficients \todo{as per
revierwer 1} that may have arisen due to movement behavior \citep{Avgar.2016}.
To validate the predictive power of the most parsimonious habitat selection
model, we ran k-fold cross-validation for case-control studies as described in
\cite{Fortin.2009} (details in Appendix A.5).

@@

\subsection{Least-Cost Paths and Corridors}
To identify movement corridors of dispersing wild dogs, we specified source
points and calculated factorial least-cost paths (LCPs) as well as factorial
least-cost corridors (LCCs) among them \citep{Elliot.2014}. We generated source
points by overlaying the study area with a regular grid of points spaced at 100
km. We only considered those points that fell within protected areas \(>\) 700
km\textsuperscript{2}, which conforms with home-range requirements of African
wild dogs reported in \cite{Pomilia.2015}. Finally, we defined centroids as
source points for those protected areas \(>\) 700 km\textsuperscript{2} that
were not assigned any source points from the regular grid. In total, we
generated 68 source points, which resulted in 2'278 unique pairwise combinations
and therefore 2'278 unique LCPs and LCCs. We computed factorial LCPs and LCCs
between source points using the R-package \textit{gdistance} (for further
details see Appendix A.7). After computation, we tallied overlapping LCPs and
LCCs, respectively, into single connectivity maps.

\section{Results}
\subsection{Dispersal Events}
In total, we collected 4'169 GPS relocations during dispersal (Figure S2 \&
Table S1), resulting in an average of 261 (\(SD\) = 207) locations per
dispersing coalition. Coalitions on average dispersed for 48 days (\(SD\) =
44), covered a mean euclidean distance of 54 km (\(SD\) = 71) and a cumulative
distance of 597 km (\(SD\) = 508). One female coalition dispersed far east into
the Hwange Hwange National Park and covered a cumulative distance of over 360 km
in under 9 days.\todo{Editor desired a quick summary of the dispersal data.}

\subsection{Habitat Selection Model}
Our most parsimonious habitat selection model (\(\Delta AIC > 2\) than any
alternative model; Table S4) retained the covariates \textit{water},
\textit{distance to water}, \textit{trees}, \textit{shrubs/grassland}, and
\textit{human influence}, beside the fixed covariates \textit{cos(ta)} and
\textit{log(sl)} (\Cref{PermeabilityResults}a). The positive coefficient for
\(log(sl)\) (\(\beta\) = 0.06, 95\% CI = 0.02 to 0.09) showed that our initial
(selection-biased) gamma distribution produced step-lengths slightly shorter
than a selection-free gamma distribution would. Similarly, the positive
coefficient for \(cos(ta)\) (\(\beta\) = 0.14; 95\% CI = 0.07 to 0.21) indicates
that our uniform distribution for turning angles produced turning angles with
too little directionality. \todo{Reviewer 1 nicely explained that the
coefficients for log(sl) and cos(ta) imply that the initial distributions were
selection-biased} With respect to environmental covariates, dispersers avoided
moving through water (\(\beta\) = -0.52, 95\% CI -0.77 to -0.26) but selected
for locations in its vicinity, although the latter effect was not significant
(\(\beta\) = -0.32, 95\% CI = -0.72 to 0.08). Dispersers avoided areas that were
densely covered by trees (\(\beta\) = -0.31, CI = -0.46 to -0.15) and preferred
areas covered by shrubs/grassland (\(\beta\) = 0.25, 95\% CI = 0.07 to 0.42).
Finally, dispersers avoided areas that were influenced by humans (\(\beta\) =
-0.41, 95\% CI = -0.78 to -0.05). With the exepction of \textit{DistanceToWater}
(\(SD_{RE}\) = 0.57), random effects revealed little variability in different
dispersal coalitions' selection strengths (i.e. \(SD_{RE} \leq 0.22\), Figure
S7).\todo{Reviewer 1 desired more information on the random effects}

@@

\begin{table}[h]
  \begin{center}
  \caption{Comparison of median permeability (interquantile range in brackets)
  across countries, separated into areas within and outside the KAZA-TFCA, as
  well as within and outside formally protected areas. High values indicate high
  permeability, whereas low values correspond to low permeability.}
  \label{PermeabilityComp}
  \begin{tabular}{llllll}
    \toprule
    \multicolumn{1}{c}{} & \multicolumn{2}{c}{KAZA-TFCA} &
    \multicolumn{2}{c}{Protection Status} & \multicolumn{1}{c}{} \\
    \cmidrule(l{3pt}r{3pt}){2-3} \cmidrule(l{3pt}r{3pt}){4-5}
    Country & Inside & Outside & Protected & Pastoral & Overall\\
    \midrule
    Angola & 0.35 (0.41) & 0.12 (0.32) & 0.35 (0.41) & 0.12 (0.32) & 0.19 (0.38)\\
    Botswana & 0.24 (0.30) & 0.14 (0.16) & 0.27 (0.35) & 0.14 (0.18) & 0.18 (0.25)\\
    Namibia & 0.20 (0.30) & 0.12 (0.17) & 0.22 (0.30) & 0.10 (0.14) & 0.14 (0.24)\\
    Zambia & 0.05 (0.09) & 0.02 (0.05) & 0.04 (0.09) & 0.03 (0.05) & 0.03 (0.06)\\
    Zimbabwe & 0.06 (0.16) & 0.05 (0.04) & 0.07 (0.17) & 0.04 (0.04) & 0.05 (0.06)\\
    \hline
    Overall & 0.15 (0.29) & 0.06 (0.14) & 0.14 (0.30) & 0.06 (0.14) & 0.08 (0.21)\\
    \bottomrule
  \end{tabular}
  \end{center}
\end{table}
